---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# elgbd
<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![R-CMD-check](https://github.com/markean/elgbd/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/markean/elgbd/actions/workflows/check-standard.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/elgbd)](https://CRAN.R-project.org/package=elgbd)
<!-- badges: end -->


## Overview

elgbd performs hypothesis testing for general block designs with empirical likelihood. 
The core computational routines are implemented with the 'Eigen' 'C++' library and 'RcppEigen' interface, with 'OpenMP' for parallel computation. 
Details of the testing procedures are given in [Kim, MacEachern, and Peruggia (2023)](https://doi.org/10.1080/10485252.2023.2206919). 
This work was supported by the U.S. National Science Foundation under Grants No. [SES-1921523](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1921523) and [DMS-2015552](https://www.nsf.gov/awardsearch/showAward?AWD_ID=2015552).


## Installation

You can install the latest stable release of elgbd from CRAN.

```{r, eval = FALSE}
install.packages("elgbd")
```

### Development version

You can install the development version of elgbd from GitHub.

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("markean/elgbd")
```


## Usage
```{r eval = TRUE}
library(elgbd)
set.seed(58234)
# Analysis of variance
el_aov(formula = Sepal.Length ~ Species, data = iris)

# All pairwise comparisons
data("clothianidin")
el_pairwise(clo ~ trt | blk, data = clothianidin, B = 1000)

# Comparisons with control
el_pairwise(clo ~ trt | blk,
  data = clothianidin, control = "Naked", method = "NB", B = 50
)

# Test for equal means
el_test(clo ~ trt | blk, clothianidin,
  lhs = matrix(c(
    1, -1, 0, 0,
    0, 1, -1, 0,
    0, 0, 1, -1
  ), byrow = TRUE, nrow = 3L)
)
```
